---
title: "Data analyses"
author: "Maxwel Coura Oliveira"
date: "4/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r load-packages, echo=TRUE, message=FALSE}
library(tidyverse)
library(glmmTMB)
library(lme4)
library(lmerTest)
library(emmeans)
library(car)
library(skimr)
library(pbkrtest)
library(moderndive)
library(purrr)
library(multcomp)
library(broom.mixed)
library(glmmTMB)
```

# Weed control

## Load data

```{r load-data, echo=TRUE, message=FALSE}
dat <- read_csv("control.csv") %>%  # Enter the data
  mutate(control = control/100) %>% 
  mutate_if(is.character, as.factor) %>% 
  mutate(GPA = as.factor(GPA)) %>% 
  mutate(siteyr = str_c(Location, Year, sep = "-", collapse = NULL)) %>% 
  filter(Herbicide != "Check") %>% 
  mutate(control = ifelse(control == "0", 0.01, control)) 
```

## Skim data

```{r skim}
skim(dat)
```


## Nesting data

```{r nesting}
# Nesting data
nested_data <- dat %>% 
  group_by(crop, species, Location) %>%
  na.omit() %>% 
  filter(species == "common ragweed" | species == "grass" | species == "giant ragweed") %>% 
  nest() %>% 
  arrange(crop, species)
nested_data
```

## Fitting the model

```{r model-fit}
# Fitting linear models
nested_models <- nested_data %>% 
  mutate(model = map(data, ~ glmmTMB(control ~ Herbicide * GPA + (1|Plot), beta_family(link = "logit"), data=.x))) 
```

## Display statistics

```{r}
# Display estimated parameters, associated statistics, confidence intervals
options(scipen=999)
nested_models %>% 
  mutate(coefs = map(model, glmmTMB:::Anova.glmmTMB)) %>% 
  unnest(coefs) %>% 
  arrange(species) %>% 
  mutate(`Pr(>Chisq)` = round(`Pr(>Chisq)`, 3))
```


## Post-hoc ANOVA

```{r emmeans_function}
nested_models1 <- nested_models %>% 
  mutate(
    emmeans = pmap(
      .l = list(
        object = model, 
        specs = "Herbicide",
        type="response",
#        cont="pairwise", 
        adjust="none"
      ),
      .f = emmeans
    )
  ) 
```


## Marginal means

```{r lsmeans}
# full data frame with all means and CIs 
nested_models2 <- nested_models1 %>% 
  mutate(emm2 = map(emmeans, data.frame)) %>% 
  unnest(emm2)
#You can filter and make a data frame for each population and dat
```


## Compact letter display

```{r cld-function}
cld_function <- function(emmeans) {
  if(requireNamespace("multcomp")) {
    multcomp::cld(emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
}
}
```



```{r cld}
nested_models3 <- nested_models1 %>% 
  mutate(cld = map(emmeans, cld_function))
```

## Final result

```{r}
# here is similar to emmeans but you have letters
nested_models4 <- nested_models3 %>% 
  unnest(cld)
# You can also filter and make specific data frames
```



# Weed biomass

## Load data

```{r load-data-bio, include=FALSE}
biomass <- read_csv("biomass.csv") %>% 
  mutate(GPA = as.factor(GPA))
```

## Biomass reduction workaround

```{r}
biomass <- biomass %>% 
  mutate(biomred = 
     ifelse(crop == "corn" & Location == "Arlington" & Year == "2018", (418.8 - Biomass)/418.8, 
     ifelse(crop == "corn" & Location == "Arlington" & Year == "2019", (30.38115	 - Biomass)/30.38115,
     ifelse(crop == "corn" & Location == "Janesville" & Year == "2018", (539.2 - Biomass)/539.2,
     ifelse(crop == "soybean" & Location == "Arlington" & Year == "2018", (108.8 - Biomass)/108.8, 
     ifelse(crop == "soybean" & Location == "Arlington" & Year == "2019", (101.12	 - Biomass)/101.12,
     ifelse(crop == "soybean" & Location == "Janesville" & Year == "2018", (316.8	 - Biomass)/316.8, NA))))))) %>% 
  mutate(biomred = ifelse(biomred < 0, 0.001, 
                    ifelse(biomred >= 0.99, 0.999, biomred))) %>% 
  filter(Herbicide != "Check") 

```


## Nesting data


```{r nest-2}
# Nesting data
nested_data <- biomass %>% 
  group_by(crop, Location) %>%
  nest() %>% 
  arrange(crop, Location)
nested_data
```

## Fitting the models

```{r model-fit-2}
# Fitting linear models
bio_models <- nested_data %>% 
  mutate(model = map(data, ~ glmmTMB(biomred ~ Herbicide * GPA + (1|Plot), beta_family(link = "logit"), data=.x))) 
nested_models
```


## Model statistics

```{r stats-2}
# Display estimated parameters, associated statistics, confidence intervals
bio_models %>% 
  mutate(coefs = map(model, glmmTMB:::Anova.glmmTMB)) %>% 
  unnest(coefs) 
```


## Post-hoc ANOVA

```{r emmeans_function-2}
bio_models1 <- bio_models %>% 
  mutate(
    emmeans = pmap(
      .l = list(
        object = model, 
        specs = "Herbicide",
        type="response",
#        cont="pairwise", 
        adjust="none"
      ),
      .f = emmeans
    )
  ) 
```


## Marginal means

```{r lsmeans-2}
# full data frame with all means and CIs 
bio_models2 <- bio_models1 %>% 
  mutate(emm2 = map(emmeans, data.frame)) %>% 
  unnest(emm2)
#You can filter and make a data frame for each population and dat
```

## Compact letter display

```{r cld-function-2}
cld_function <- function(emmeans) {
  if(requireNamespace("multcomp")) {
    multcomp::cld(emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
}
}
```


```{r cld-2}
bio_models3 <- bio_models1 %>% 
  mutate(cld = map(emmeans, cld_function))
```

## Final results

```{r}
# here is similar to emmeans but you have letters
bio_models4 <- bio_models3 %>% 
  unnest(cld)
# You can also filter and make specific data frames
```




# Figures



```{r}
# a ggplot function
source("element_textbox_highlight.R")
```



## Combining control and biomass reduction

```{r}
bio_models4 %>% 
  rename(biomass = response) %>%
  dplyr::select(-data, -model, -emmeans, -df, -SE, .group) -> bio_models5

nd_dt <- nested_models4 %>% 
  dplyr::select(crop, Location, Herbicide, species, response, lower.CL, upper.CL, .group)


nested_models4 %>% 
  dplyr::select(-data, -model, -df, -emmeans, -SE, -.group) %>% 
  pivot_wider(id_cols = c("crop", "Location", "Herbicide"), 
              names_from = "species", values_from = "response") %>% 
  left_join(bio_models5, by = c("crop", "Location", "Herbicide")) %>% 
  pivot_longer(cols = c("common ragweed", "giant ragweed", "grass", "biomass"),
               names_to = "species", values_to = "response") %>% 
  mutate(letters = .group) %>% 
  dplyr::select(-.group) %>%
  mutate(lower.CL = case_when(
    species == "biomass" ~ lower.CL,
    TRUE ~ NA_real_
  ),
  upper.CL = case_when(
    species == "biomass" ~ upper.CL,
    TRUE ~ NA_real_
  ),
    letters = case_when(
    species == "biomass" ~ letters,
    TRUE ~ NA_character_)) %>% 
  left_join(nd_dt, by = c("crop", "species", "Location", 
                          "Herbicide", "response")) %>% 
  unite("lower.CL", c("lower.CL.x", "lower.CL.y"), sep = "", na.rm = TRUE) %>% 
  unite("upper.CL", c("upper.CL.x", "upper.CL.y"), sep = "", na.rm = TRUE) %>% 
  unite("letters", c("letters", ".group"), sep = "", na.rm = TRUE) %>% 
  mutate_at(c("lower.CL", "upper.CL"), as.double) -> all_data
```


## Soybeans

### Tidy names

```{r}
all_data %>% 
  filter(!is.na(response)) %>% 
  mutate(species = fct_recode(species,
                              "Biomass reduction" = "biomass")) %>% 
  mutate(species = fct_relevel(species,
                               levels = "common ragweed", "giant ragweed", "grass",
                               "Biomass reduction")) %>% 
  mutate(Herbicide = fct_recode(Herbicide,
                                "metribuzin + chlorimuron-ethyl " = 
                                  "Canopy DF",
                                "flumioxazin + pyroxasulfone" = 
                                  "Fierce",
                                "dimethenamid-P + saflufenacil" = 
                                  "Verdict"))  %>% 
  filter(crop == "soybean") -> all_data1
```

### Figure

```{r}
all_data1 %>% 
  ggplot(aes(x = fct_reorder(Herbicide, response), y = response, 
             color = Herbicide)) +
  geom_point(size = 2, show.legend = FALSE) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  geom_text(aes(label = letters), nudge_y = 0.001, nudge_x = 0.3) +
  facet_wrap(Location ~ species, drop	= TRUE, as.table = TRUE) +
  scale_y_continuous(limits = c(0., 1), breaks = c(0, 0.25, 0.50, 0.75, 1),
                     labels = scales::percent_format(scale = 100, 
                                                     accuracy = 1,
                                                     suffix = "")) +
  geom_jitter(data = biomass %>% 
                mutate(species = "Biomass reduction") %>% 
                dplyr::select(- Year) %>% 
                filter(crop == "soybean" & species %in% "Biomass reduction") %>% 
                rename(response = biomred) %>% 
                mutate(Herbicide = fct_recode(Herbicide,
                                "metribuzin + chlorimuron-ethyl " = 
                                  "Canopy DF",
                                "flumioxazin + pyroxasulfone" = 
                                  "Fierce",
                                "dimethenamid-P + saflufenacil" = 
                                  "Verdict")), 
              alpha = 0.1)  + 
  geom_jitter(data = dat %>% 
                filter(crop == "soybean" & species %in% c("grass", "common ragweed", 
                                                          "giant ragweed")) %>% 
                dplyr::select(- Year) %>% 
                rename(response = control) %>% 
                mutate(Herbicide = fct_recode(Herbicide,
                                "metribuzin + chlorimuron-ethyl " = 
                                  "Canopy DF",
                                "flumioxazin + pyroxasulfone" = 
                                  "Fierce",
                                "dimethenamid-P + saflufenacil" = 
                                  "Verdict")), 
              alpha = 0.1)  + 
  theme_test() +
  labs(y = "%",
       x = "") +
#       title = "Figure 2. Efficacy (%) of preemergence herbicides in soybean at Arlington and Janesville, WI",
#       subtitle = "Weed biomass reduction (%) and control (%) of common ragweed, giant ragweed and grass are pooled over carrier volume rates"

  coord_flip() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
        plot.title = element_markdown(size = 12, hjust = 0.99),
        plot.subtitle = element_markdown(size = 8, hjust = 1),
        text  = element_text(family = "Arial", color = "#282728"),
        axis.text.y = element_markdown(),
        axis.text.x = element_markdown(),
        strip.background = element_blank(),
    strip.text = element_textbox_highlight(
      family = "Arial", size = 12, face = "bold",
      fill = "white", box.color = "chartreuse4", color = "chartreuse4",
      halign = .5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(5, 0, 3, 0), margin = margin(0, 1, 3, 1),
      hi.labels = c("Biomass reduction", "grass", "common ragweed", "giant ragweed"),
      hi.fill = "chartreuse4", 
      hi.box.col = "black", hi.col = "#282728"
    ))
  ggsave("soybean.pdf", width = 7, device = cairo_pdf,
       height = 5, dpi = 600) 
```



## Corn


### Tidy names

```{r}
all_data %>% 
  filter(!is.na(response)) %>% 
  mutate(species = fct_recode(species,
                              "Biomass reduction" = "biomass")) %>% 
  mutate(species = fct_relevel(species,
                               levels = "common ragweed", "giant ragweed", "grass",
                               "Biomass reduction")) %>% 
  mutate(Herbicide = fct_recode(Herbicide,
                                "bicyclopyrone + mesotrione + *S*-metolachlor" = 
                                  "Acuron Flexi",
                                "fluthiacet-methyl + pyroxasulfone" = "Anthem Maxx",
                                "acetochlor + clopyralid + mesotrione" = "Resicore"))  %>% 
  filter(crop == "corn") -> all_data2
```

```{r}
#remove data points from Janesville grass
all_data2 %>% 
  ungroup(Location) %>% 
  mutate(id = row_number()) %>% 
  filter(!id %in% c(11, 14, 17)) -> all_data2
```



### Figure

```{r}
ann_text1 <- data.frame(Herbicide = "bicyclopyrone + mesotrione + *S*-metolachlor", 
                        response = 0.5, lab = "Text",
                       Location = factor("Janesville", levels = c("Arlington", "Janesville")),
                       species = factor("grass", levels = c("common ragweed", 
                                                            "Biomass reduction",
                                                            "giant ragweed", 
                                                            "grass")))
ann_text2 <- data.frame(x = "fluthiacet-methyl + pyroxasulfone", 
                        xend = "fluthiacet-methyl + pyroxasulfone",
                       y=0.4, yend=0.6, 
                       Location = factor("Janesville", levels = c("Arlington", "Janesville")),
                       species = factor("grass", levels = c("common ragweed", 
                                                            "Biomass reduction",
                                                            "giant ragweed", 
                                                            "grass")))
```


```{r}
fig_1 <- all_data2 %>% 
  ggplot(aes(x = fct_reorder(Herbicide, response), y = response, 
             color = Herbicide)) +
  geom_point() +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL)) +
  geom_text(aes(label = letters), nudge_y = 0.001, nudge_x = 0.3) +
  facet_wrap(Location ~ species) +
  scale_y_continuous(limits = c(0., 1), breaks = c(0, 0.25, 0.50, 0.75, 1),
                     labels = scales::percent_format(scale = 100, 
                                                     accuracy = 1,
                                                     suffix = "")) +
  geom_jitter(data = biomass %>% 
                mutate(species = "Biomass reduction") %>% 
                mutate(id = row_number()) %>% 
                dplyr::select(- Year) %>% 
                filter(crop == "corn" & species %in% "Biomass reduction") %>% 
                rename(response = biomred) %>% 
                mutate(Herbicide = fct_recode(Herbicide,
                                "bicyclopyrone + mesotrione + *S*-metolachlor" = "Acuron Flexi",
                                "fluthiacet-methyl + pyroxasulfone" = "Anthem Maxx",
                                "acetochlor + clopyralid + mesotrione" = "Resicore")), 
              alpha = 0.15)  + 
  geom_jitter(data = dat %>% 
                filter(crop == "corn" & species %in% c("grass", "common ragweed", 
                                                          "giant ragweed")) %>% 
                dplyr::select(- Year) %>% 
                  mutate(response = case_when(Location == "Janesville" & 
                                species == "grass" & 
                                 crop == "corn" ~ NA_real_,
                              TRUE  ~ control)) %>% 
                  mutate(Herbicide = fct_recode(Herbicide,
                                "bicyclopyrone + mesotrione + *S*-metolachlor" = 
                                  "Acuron Flexi",
                                "fluthiacet-methyl + pyroxasulfone" = "Anthem Maxx",
                                "acetochlor + clopyralid + mesotrione" = "Resicore")), 
              alpha = 0.15)  + 
  geom_text(data = ann_text1, 
            label = "Carrier volume\n × \n PRE herbicide\n interaction",
            color = "#282728") +
  geom_segment(data = ann_text2,
               aes(x=x,y=y,yend=yend,xend=xend),
               arrow = arrow(length = unit(0.1,"cm")),
               inherit.aes=FALSE)+
  theme_test() +
  labs(y = "%",
       x = "",
       title = "Figure 1. Efficacy (%) of preemergence herbicides in corn at Arlington and Janesville, WI",
       subtitle = "Weed biomass reduction (%) and control (%) of common ragweed, giant ragweed and grass are pooled over carrier volume rates") +
  coord_flip() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "none",
#        plot.title = element_markdown(size = 12, hjust = 0.99),
#        plot.subtitle = element_markdown(size = 8, hjust = 1),
        plot.title = element_blank(),
        plot.subtitle = element_blank(),
        text  = element_text(family = "Arial", color = "#282728"),
        axis.text.y = element_markdown(),
        axis.text.x = element_markdown(),
        strip.background = element_blank(),
    strip.text = element_textbox_highlight(
      family = "Arial", size = 12, face = "bold",
      fill = "white", box.color = "chartreuse4", color = "chartreuse4",
      halign = .5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(5, 0, 3, 0), margin = margin(0, 1, 3, 1),
      hi.labels = c("Biomass reduction", "grass", "common ragweed", "giant ragweed"),
      hi.fill = "chartreuse4", 
      hi.box.col = "black", hi.col = "#282728"
    )) +
  ggsave("corn.png", width = 8, #device = cairo_pdf,
       height = 5, dpi = 600) 
```









## Interaction


```{r}
#nested_models$crop[[2]]
nested_models$model[[4]] %>% 
#  emmip(~ GPA |Herbicide) 
  emmeans(~   GPA | Herbicide, type="response") %>% 
  cld(Letters=letters, adjust="none", reversed = TRUE) %>% 
  as_tibble() -> grass_cn_j
```

### Figure

```{r}
fig_2 <- grass_cn_j %>% 
  mutate(Location = "Janesville") %>% 
  mutate(gpa_1 = as.character(GPA)) %>% 
  mutate(gpa_1 = glue::glue("{gpa_1} GPA")) %>% 
  mutate(gpa_1 = fct_relevel(gpa_1, levels = 
                               c("2.5 GPA", "5 GPA",
                                 "10 GPA", "15 GPA",
                                 "17.5 GPA"))) %>% 
  mutate(Herbicide = fct_recode(Herbicide,
                                "bicyclopyrone + mesotrione + *S*-metolachlor" = "Acuron Flexi",
                                "fluthiacet-methyl + pyroxasulfone" = "Anthem Maxx",
                                "acetochlor + clopyralid + mesotrione" = "Resicore"))  %>% 
  unite("trt", c("Herbicide", "gpa_1"), sep = " ", remove = FALSE) %>% 
  ggplot(aes(x = GPA, y = response, 
              color = GPA)) +
  coord_flip() +
  geom_jitter(data = dat %>% 
                filter(species == "grass") %>% 
                filter(crop == "corn" & Location == "Janesville") %>% 
                rename(response = control) %>% 
                mutate(Herbicide = fct_recode(Herbicide,
                                "bicyclopyrone + mesotrione + *S*-metolachlor" = "Acuron Flexi",
                                "fluthiacet-methyl + pyroxasulfone" = "Anthem Maxx",
                                "acetochlor + clopyralid + mesotrione" = "Resicore")), 
              alpha = 0.15)  + 
  geom_point(size=2) +
  geom_linerange(aes(ymin = lower.CL, ymax = upper.CL),
                 size = 1) +
  facet_wrap(~ Herbicide, ncol = 1) +
  scale_color_brewer(palette = "Dark2") +
  labs(y = "Grass control (%)",
#       title = "Arlington Carrier volume × PRE herbicide",
       x = expression(paste("Carrier volume (gallons acre"^"-1",")"))) +
  geom_text(aes(label = .group), nudge_y = 0.006, nudge_x = 0) +
  scale_y_continuous(limits = c(0.94, 1), breaks = c(0.94, 0.96, 0.98, 1),
                     labels = scales::percent_format(scale = 100, 
                                                     accuracy = 1,
                                                     suffix = "")) +
  theme_test() +
  theme(legend.position = "none",
       text  = element_text(family = "Arial", color = "#282728"),
       plot.subtitle = element_markdown(size = 7, margin = margin(-2, 2, -8, 2)),
        axis.text.y = element_markdown(),
        strip.background = element_blank(),
      strip.text = element_textbox_highlight(
      family = "Arial", size = 8, face = "bold",
      fill = "white", box.color = "chartreuse4", color = "chartreuse4",
      halign = .5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
      padding = margin(2, 2, 2, 2), margin = margin(6, 1, 4, 1),
      hi.labels = c("acetochlor + clopyralid + mesotrione", 
                    "bicyclopyrone + mesotrione + *S*-metolachlor",
                    "fluthiacet-methyl + pyroxasulfone"),
      hi.fill = "chartreuse4", 
      hi.box.col = "black", hi.col = "white"
    )) +
  ggsave("grass_weeds.png", width = 3, #device = cairo_pdf,
       height = 9, dpi = 600) -> b
```

       
### Combining figures

```{r}
library(patchwork)
```

```{r}
fig_3 <- wrap_elements(grid::textGrob('Text on left side')) / fig_2 +
  plot_layout(heights = c(1, 100))
```


```{r warning=FALSE}
combined <- fig_1 + fig_2 + 
  plot_layout(widths = c(3, 1))  #+
#   plot_annotation(title = "Figure 1. Efficacy (%) of preemergence herbicides in corn at Arlington and Janesville, WI",
#       subtitle = "Weed biomass reduction (%) and control (%) of common ragweed, giant ragweed and grass are pooled over carrier volume rates, except to grass control in \nArlington",
#       theme = theme(plot.subtitle = element_text(size = 10)))


ggsave("corn_2.pdf", device = cairo_pdf,
       width = 10, height = 5, dpi = 600, combined)
```

